\section{Summary}

We covered the complete design of OlaVM in previous sections, including VM design, ZKVM constraint design, constraint ideas, logic behind each module and much more. We believe that this content will give a fundamental understanding of ZKVM design process. Due to the limited space, we are working on a new, detailed, ``module by module'' paper, focused on the subsequent engineering implementation process, which includes the design on how to support further EVM instructions in OlaVM. Related ZKVM technologies are under constant development and we continuously keep up to date with recent research, such as new ZK-friendly Hash and more efficient Lookup Argument \cite{cryptoeprint:2022/621}, in order to include this in OlaVM design.

In addition to this, we want to show our gratitude for the hard work of all the prominent teams in the space of Zero Knowledge, of which, naming a few, PSE, Matter Labs, Polygon Hermez and StarkWare. We have learnt a lot through their contributions in open source documentation, code and online sharing amongst other, on how to design, improve ZK-efficiency and construct a ZKVM. We want to direct a special thanks towards Justin Drake\footnote{\url{https://twitter.com/drakefjustin}}, Barry Whitehat\footnote{\url{https://twitter.com/barrywhitehat}} and others, whom we've had educational and inspirational information exchanges with, enlightening us on certain aspects in ZKEVM design, providing us with a better understanding on how to proceed. On an ending note, there is still a lot to be done, research to be conducted, knowledge to be acquired and room for improvement to be identified.
