\subsection{Signature}

We support two different signature schemes, ECDSA \cite{Johnson99theelliptic} and Schnorr \cite{jofc-1991-14302}.

\subsubsection{ECDSA Signature}

The hash function we choose is Sinsemilla Hash, which is the same function used in signature generation. With the following notations:
\begin{itemize}
    \item $(r, s)$ is the signature.
    \item $m$ is the message to verify.
    \item $Q(Q_x, Q_y)$ is the public-key curve point.
    \item $h$ is the hash result of $m$.
    \item $G$ is the elliptic curve base point.
    \item $n$ is the order of $G$.
    \item $\mathcal{O}$ is the identity element.
    \item $L_n$ is the bit length of $n$.
\end{itemize}

The constraints are the following:
\begin{enumerate}
    \item Check that $Q$ is not equal to $\mathcal{O}$.
    \item Check that $Q$ lies on the curve, which means: $Q_y^2 = Q_x^3+\alpha Q_x + \beta$.
    \item Check that $nQ = \mathcal{O}$.
    \item Check that $r$ and $s$ are in $[1, n-1]$.
    \item Let $z$ be the leftmost $L_n$ bits of $h$ (we use Sinsemilla Hash builtin circuit to check $h \equiv \mathrm{HASH}(m)$).
    \item Calculate $u_1 = zs^{-1} \bmod n$ and $u_2 = rs^{-1} \bmod n$.
    \item Calculate curve point $(x_1,y_1) = u_1 G + u_2 Q$, check $(x_1, y_1) \ne \mathcal{O}$.
    \item Check that $r \equiv x_1 \pmod n$.
\end{enumerate}

\subsubsection{Schnorr Signature}

Schnorr signature is known for its simplicity, Bitcoin used Schnorr signature as well. The hash function we choose is Sinsemilla Hash. With the following notations:
\begin{itemize}
    \item $(s, e)$ is the signature.
    \item $m$ is the message to verify, it is represented as list of finite bit strings.
    \item $h$ is the hash result of $m$.
    \item $g$ is the generator.
    \item $y$ is the public verification key.
\end{itemize}

The constraints are the following:
\begin{enumerate}
    \item Check $r_v = g^s y^e$.
    \item Check $e_v = \mathrm{Hash}(r_v \mathbin{||} m)$, where $||$ denotes concatenation, $r_v$ is represented as a bit string (Like above, we use Sinsemilla Hash builtin circuit to check it).
    \item Check that $e_v \equiv e$.
\end{enumerate}

\vspace{3mm}
Schnorr signature also supports Multi-Signatures \cite{cryptoeprint:2018/068}, which could provide more security. Given
\begin{itemize}
    \item A list of public keys $L = \{X_1, X_2, \ldots, X_n\}$.
    \item An aggregated public key $X = \prod_{i=1}^n H(L, X_i) X_i$.
    \item A message $m$.
    \item A signature $(R, s)$.
    \item A list of random numbers $R_i = g^{r_i}$ and $R=\prod_{i=1}^n R_i$.
\end{itemize}

The constraints are the following:
\begin{enumerate}
    \item Check $c = \mathrm{Hash}(X, R, m)$ (As always, this can be done in Hash builtin circuit).
    \item Check $u = c X$.
    \item Check $s G \equiv R + u$.
\end{enumerate}
