\section{Structure of Execution Trace Table} \label{sec:structure-of-execution-trace-table}

As an initial step, by dividing the instructions, data and other contents involved in the program execution trace into one main trace and multiple sub traces we are able to prove that the program is being executed correctly. There is a hierarchical relationship between these sub traces and the main trace. When there are instructions that cannot be processed in the main trace, these instructions will be executed in a sub trace. These sub traces are associated with the main trace through Lookup Argument. The complexity of polynomial representation of the main trace table has been reduced and the speed of proof generation is improved through this division of main and sub traces.

This section primarily introduces the main trace table and the RAM trace table, and others like arithmetic sub trace table, binary sub trace table will be introduced in other sections.

In this section you'll find a description of the main trace table and RAM trace table, before that we've listed a few variables that will be referenced to. Some variables that have been described in Section \ref{subsec:instruction-structure} will not be repeated below.
\begin{itemize}
    \item \verb|clk|: The global clock of the program execution tracking. Every time an instruction is executed, \verb|clk| automatically increases by 1;
    \item \verb|instruction|: The encoded representation of an instruction;
    \item \verb|pc|: A program counter. Under normal circumstances, the \verb|pc| update logic is: \verb|pc = pc + instruction_size|, in other cases, such as \verb|flow_op|, the \verb|pc| will be changed according to the corresponding logic;
    \item \verb|fp|: Special register used in \verb|CALL| and \verb|RET| instructions, stores a pointer to the RPR memory location;
    \item \verb|const|: Used to store the immediate value of the instruction;
    \item \verb|r0|, \verb|r1|, \verb|r2|: Three general-purpose registers used for the storage of instruction input and output data;
    \item \verb|carry|: Indicates whether there is a carry;
    \item \verb|address|: The address operated by RAM instructions;
    \item \verb|value|: The value operated by RAM instructions;
    \item \verb|oldRoot|: World state representation of Verkle Tree before update;
    \item \verb|newRoot|: World state representation of Verkle Tree after update.
\end{itemize}

\input{execution-trace-table/main-trace-table}
\input{execution-trace-table/ram-trace-table}
